manuscript_analysis

### 2024-07-03 manuscript_analysis.Rmd
rerunning for typo models from 1-3

#df1 and df2 are the fastest ones
# predictions() can also be used directly with df_models -> takes longer

# DO NOT RUN NOW, RUN LATER!
predictions_depth_temp(df_1)
predictions_depth_temp(df_2)
predictions_depth_temp(df_3)
# 4 not run yet, will wait with this
predictions_depth_temp(df_4)

@@

# total_models |> 
#   filter(tot_abu > 20) |> 
#   distinct(Species, tot_abu)
stats_gamms(total_models)

>>>>

#df1 and df2 are the fastest ones
# predictions() can also be used directly with df_models -> takes longer
# BECAUSE OF TYPO: RE RUN TEMP + DEPTH models from df1-3, df4 still needs to be run & stats overview too

df_1to3_dept_temp <- bind_rows(df_1, df_2, df_3) |> 
  filter(tot_abu > 20)

df_1to3_dept_temp |> 
  distinct(Species)

predictions_depth_temp(df_1to3_dept_temp)
# DO NOT RUN NOW, RUN LATER!
predictions_depth_temp(df_1)
predictions_depth_temp(df_2)
predictions_depth_temp(df_3)
# 4 not run yet, will wait with this
predictions_depth_temp(df_4)

stats_gamms(df_test)

@@

stats_gamms(total_models)
